Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-10 papers/ms.tex
update ms
cleanup tex

% {\bf TODO RONAN: PLEASE VET ENTIRE SECTION, AND UPDATE WHERE
% APPROPRIATE!}.

@@

We selected stars suitable for gyrochronology by requiring $\bpmrpo
\geq 0.5$ to focus on FGKM stars that experience magnetic braking.
For TESS, we also restricted our sample to $G<16$, to ensure the stars
are bright enough to extract usable light curves from the full-frame
images (FFIs).  The magnitude cut corresponds to $\bpmrpo < 2.6$
($\sim$M3V) at the relevant distances.  These cuts gave 19 stars in
CH-2 and 42 stars in RSG-5.  We extracted light curves from the TESS
images using the \texttt{unpopular} package
\citep{hattorio_2021_cpm}, and regressed them against systematics with
its causal pixel model.  We measured rotation periods using
Lomb-Scargle periodograms and visually vetted the results using an
interactive program that allows us to switch between TESS Cycles,
select particular sectors, flag stars with multiple periods, and
correct half-period harmonics. For ZTF, we used the same color cut to
focus on FGKM stars, but restricted the sample to $13 < G < 18$ to
avoid the saturation limit on the bright end and ensure sufficient
photometric precision at the faint end. We followed the procedure
outlined in \citet{curtis_rup147_2020}: we downloaded $8'\times8'$
image cutouts, ran aperture photometry for the target and neighboring
stars identified with Gaia, and used them to define a systematics
correction to refine the target light curves. 
%Like for TESS, we also
%calculated periods with Lomb-Scargle periodograms using an interactive
%program that allows us to visually validate our measurements.
%{\bf How many stars with periods from TESS? ZTF? Overlap?
%Consistency? }

@@

% {\bf TODO verify continuum normalization in Li EW measurement...}
% Given the reddening-corrected color of the star this is
% consistent(ish) with the Pleiades/NGC2516 based on my NGC2516 figure.
% But it looks sub-IC2602 based on the lithium.png figure, which uses
% the Randich2018 values.
% It's pretty clearly super-field.
% I really need to verify the continuum normalization.
% COMPARE vs:
% \citealt{randich_gaiaeso_2018}).  
% \citet{berger_identifying_2018}

\paragraph{High-Resolution Imaging}
% KOI-6186 & 58662.62 &   Kp     &  4 &   80.00 &  4.1 &  4.8 &  5.4 &  5.8 &  6.5 &  6.8 &  7.6 &  8.3 &  8.2 &  8.3 &             Petigura \\ % N2.20190628.53389
We acquired adaptive optics imaging of Kepler-1643 on the night of
2019 June 28 using the NIRC2 imager on Keck-II.
Using the narrow camera (FOV = 10.2\arcsec), we obtained 4 images in
the $K'$ filter ($\lambda = 2.12\,\mu$m) with a total exposure time of
320\,s. We analyzed these data following \citet{kraus_impact_2016},
and determined the detection limits to visual companions by analyzing
the residuals after subtracting an empirical PSF template. 
This procedure yielded contrast limits of $\Delta K' = 4.1$ mag at
$\rho = 150$ mas, $\Delta K' = 5.8$ mag at $\rho = 300$ mas, and
$\Delta K' = 8.3$ mag at $\rho > 1000$ mas.

@@

\paragraph{High-Resolution Imaging}
% KOI-7368 & 58646.57 &   Kp     &  4 &   80.00 &  5.2 &  5.8 &  6.4 &  6.7 &  7.1 &  7.5 &  8.1 &  8.7 &  8.7 &  8.8 &                Huber \\ % N2.20190612.49290
We acquired adaptive optics imaging of KOI-7368 on the night of 2019
June 12, again using NIRC2.  The
observational configuration and reduction was identical as for
Kepler-1643.  No companions were detected, and the analysis of the
image residuals yielded contrast limits of $\Delta K' = 5.2$ mag at
$\rho = 150$ mas, $\Delta K' = 6.7$ mag at $\rho = 300$ mas, and
$\Delta K' = 8.7$ mag at $\rho > 1000$ mas.

@@

\paragraph{Binarity}

%(e.g., Jenkins KSCI-19081-002 KPDH pp 129, or many other pages)
KOI-7913 is almost certainly a binary. %\footnote{Relevant identifiers for the
%primary are KIC 8873450 = Gaia DR2/EDR3 2106235301785454208.  For the
%secondary, they are KIC 8873448 = Gaia DR2/EDR3 2106235301785453824.}
The north-west primary is $\approx$0.5 magnitudes brighter than the
south-east secondary in optical passbands.  The two stars are
separated in Gaia EDR3 by $3\farcs5$ on-sky, and have parallaxes
consistent within $1$-$\sigma$ (with an average $\varpi=3.66 \pm
0.01$\,mas).  The apparent on-sky separation is
$959 \pm 2$ au.  
The Gaia EDR3 proper motions are also nearly identical.
%$(\mu_{\alpha'},\mu_\delta)=(2.439\pm0.015, 1.009\pm 0.016)\,{\rm
%mas}\,{\rm yr}^{-1}$ for the primary, and
%$(\mu_{\alpha'},\mu_\delta)=(2.696\pm0.020, 0.650 \pm 0.021) \,{\rm
%mas}\,{\rm yr}^{-1}$ for the secondary.  
Since two stars were resolved
in the Kepler Input Catalog and are roughly one Kepler pixel apart, an
accurate crowding metric has already been applied in the NASA Ames
data products to correct the mean flux level
\citep{2017ksci.rept....6M}.  This is important for deriving accurate
transit depths.

\paragraph{Spectra}

We acquired Keck/HIRES spectra for KOI-7913 A on the night of 2021 Nov
13, and KOI-7913 B on the night of 2021 Oct 26.  The 
\texttt{SpecMatch-Emp} \citep{yee_SM_2017} machinery yielded $T_{\rm
eff,A} = 4324 \pm 70\,{\rm K}$, $T_{\rm eff,B} = 4038 \pm 70\,{\rm
K}$.  The remaining parameters were in agreement with those from the
cluster isochrone.  For the primary, we also found $[{\rm Fe/H}]=
-0.06 \pm 0.09$, $v\sin i = 13.3 \pm 1.0\,\mkms$, and ${\rm RV}_{\rm
sys} = -17.8 \pm 1.1\,\mkms$.  For the secondary, these same parameters
were $[{\rm Fe/H}]= -0.01 \pm 0.09$, $v\sin i = 10.7 \pm 1.0\,\mkms$,
and ${\rm RV}_{\rm sys} = -18.8 \pm 1.1\,\mkms$.
Neither of the KOI-7913 components shows strong lithium absorption,
but this is expected given their $\approx$K6V and $\approx$K8V
spectral types.
They do however both show H$\alpha$ in emission.
We discuss the significant in greater depth in Appendix~\ref{app:spectra},
but broadly speaking both observations are consistent with
a $\approx$40 Myr age for KOI-7913.

\paragraph{High-Resolution Imaging}

We acquired adaptive optics imaging of KOI-7913 on the night of 2020
Aug 27 using the NIRC2 imager.  The
observational configuration and reduction was identical as before.
The images showed KOI-7913 A, KOI-7913 B, and an additional faint star
$\approx$$0\farcs99$ due East of KOI-7913 B.  Applying the PSF-fitting
routines from \citet{kraus_impact_2016}, the tertiary star has a
separation $\rho = 4397 \pm 3$\,mas from the primary, at a position
angle $231.17^\circ \pm 0.02^\circ$, with a $\Delta K' = 6.97 \pm
0.04$.  While it is too faint to affect the interpretation of the KOI
itself, it would be amusing if the faint neighbor were also comoving
and young -- at the age of the system, it would have a mass roughly
between 10 and 15\,M$_{\rm Jup}$.  Additional imaging epochs will 
tell.

@@

\paragraph{Kepler-1643}
  %Based on the Q1-Q17 DR25 False Positive Probability table hosted at
%the NASA Exoplanet Archive, 
Kepler-1643~b (KOI-6186.01) was already validated as a transiting
planet by \citet{morton_false_2016}, who found a probability for any
of the aforementioned false positive scenarios of 9$\times$10$^{-6}$.
Repeating the calculation with our own stellar-variability correction
and the new NIRC2 imaging constraints, we find ${\rm FPP} =
6\times10^{-9}$, where the improvement is due to the new NIRC2
contrast curves.  Figure~\ref{fig:planets} shows the justification:
the transit is flat and has a high S/N ($\approx 47$), which is
difficult to reproduce with eclipsing binary models.

@@

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``candidate''
planet.  \citet{morton_false_2016} did not compute a false positive
probability for the system because their default trapezoidal fitting
routine failed, presumably due to the spot-induced variability.
%The Q1-Q17 DR25 False Positive Probability table however lists its
%probability of being an astrophysical false positive as ``1.0''. Given
%that none of the other columns in the table are populated, this seems
%likely to be a database entry error ({\bf ask Jessie}). 
Our fitting approach rectifies this point, and our new NIRC2 images
revealed no new stellar companions.  Performing the validation
calculation, we find ${\rm FPP} \approx 4\times10^{-3}$.  Though not
as convincing as Kepler-1643, this formally clears the usual threshold
for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit is
$\approx$$32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve (see Figure~\ref{fig:planets}).
The positional probability score also meets the requirements
for transiting sources thought to share positions with their
target stars \citep{morton_false_2016,2017ksci.rept...16B}. 
%A visual inspection of
%each individual transit also shows a weak notch at the predicted
%transit times; over the 198 observed transits, the resulting signal
%seems sensible.

>>>>

@@

We selected stars suitable for gyrochronology by requiring $\bpmrpo
\geq 0.5$ to focus on FGKM stars that experience magnetic braking.
For TESS, we also restricted our sample to $G<16$, to ensure the stars
are bright enough to extract usable light curves from the full-frame
images (FFIs).  The magnitude cut corresponds to $\bpmrpo < 2.6$
($\sim$M3V) at the relevant distances.  These cuts gave 19 stars in
CH-2 and 42 stars in RSG-5.  We extracted light curves from the TESS
images using the \texttt{unpopular} package
\citep{hattorio_2021_cpm}, and regressed them against systematics with
its causal pixel model.  We measured rotation periods using
Lomb-Scargle periodograms and visually vetted the results using an
interactive program that allows us to switch between TESS Cycles,
select particular sectors, flag stars with multiple periods, and
correct half-period harmonics. For ZTF, we used the same color cut to
focus on FGKM stars, but restricted the sample to $13 < G < 18$ to
avoid the saturation limit on the bright end and ensure sufficient
photometric precision at the faint end. We followed the procedure
outlined in \citet{curtis_rup147_2020}: we downloaded $8'\times8'$
image cutouts, ran aperture photometry for the target and neighboring
stars identified with Gaia, and used them to define a systematics
correction to refine the target light curves.

@@

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of Kepler-1643 on the night of
2019 June 28 using the NIRC2 imager on Keck-II.  Using the narrow
camera (FOV = 10.2\arcsec), we obtained 4 images in the $K'$ filter
($\lambda = 2.12\,\mu$m) with a total exposure time of 320\,s. We
analyzed these data following \citet{kraus_impact_2016}, and
determined the detection limits to visual companions by analyzing the
residuals after subtracting an empirical PSF template.  This procedure
yielded contrast limits of $\Delta K' = 4.1$ mag at $\rho = 150$ mas,
$\Delta K' = 5.8$ mag at $\rho = 300$ mas, and $\Delta K' = 8.3$ mag
at $\rho > 1000$ mas.

@@

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of KOI-7368 on the night of 2019
June 12, again using NIRC2.  The observational configuration and
reduction was identical as for Kepler-1643.  No companions were
detected, and the analysis of the image residuals yielded contrast
limits of $\Delta K' = 5.2$ mag at $\rho = 150$ mas, $\Delta K' = 6.7$
mag at $\rho = 300$ mas, and $\Delta K' = 8.7$ mag at $\rho > 1000$
mas.

@@

\paragraph{Binarity}
KOI-7913 is almost certainly a binary.  The north-west primary is
$\approx$0.5 magnitudes brighter than the south-east secondary in
optical passbands.  The two stars are separated in Gaia EDR3 by
$3\farcs5$ on-sky, and have parallaxes consistent within $1$-$\sigma$
(with an average $\varpi=3.66 \pm 0.01$\,mas).  The apparent on-sky
separation is $959 \pm 2$ au.  The Gaia EDR3 proper motions are also
nearly identical.  Since two stars were resolved in the Kepler Input
Catalog and are roughly one Kepler pixel apart, an accurate crowding
metric has already been applied in the NASA Ames data products to
correct the mean flux level \citep{2017ksci.rept....6M}.  This is
important for deriving accurate transit depths.

\paragraph{Spectra}
We acquired Keck/HIRES spectra for KOI-7913 A on the night of 2021 Nov
13, and KOI-7913 B on the night of 2021 Oct 26.  The
\texttt{SpecMatch-Emp} \citep{yee_SM_2017} machinery yielded $T_{\rm
eff,A} = 4324 \pm 70\,{\rm K}$, $T_{\rm eff,B} = 4038 \pm 70\,{\rm
K}$.  The remaining parameters were in agreement with those from the
cluster isochrone.  For the primary, we also found $[{\rm Fe/H}]=
-0.06 \pm 0.09$, $v\sin i = 13.3 \pm 1.0\,\mkms$, and ${\rm RV}_{\rm
sys} = -17.8 \pm 1.1\,\mkms$.  For the secondary, these same
parameters were $[{\rm Fe/H}]= -0.01 \pm 0.09$, $v\sin i = 10.7 \pm
1.0\,\mkms$, and ${\rm RV}_{\rm sys} = -18.8 \pm 1.1\,\mkms$.  Neither
of the KOI-7913 components shows strong lithium absorption, but this
is expected given their $\approx$K6V and $\approx$K8V spectral types.
They do however both show H$\alpha$ in emission.  We discuss the
significant in greater depth in Appendix~\ref{app:spectra}, but
broadly speaking both observations are consistent with a $\approx$40
Myr age for KOI-7913.

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of KOI-7913 on the night of 2020
Aug 27 using the NIRC2 imager.  The observational configuration and
reduction was identical as before.  The images showed KOI-7913 A,
KOI-7913 B, and an additional faint star $\approx$$0\farcs99$ due East
of KOI-7913 B.  Applying the PSF-fitting routines from
\citet{kraus_impact_2016}, the tertiary star has a separation $\rho =
4397 \pm 3$\,mas from the primary, at a position angle $231.17^\circ
\pm 0.02^\circ$, with a $\Delta K' = 6.97 \pm 0.04$.  While it is too
faint to affect the interpretation of the KOI itself, it would be
amusing if the faint neighbor were also comoving and young -- at the
age of the system, it would have a mass roughly between 10 and
15\,M$_{\rm Jup}$.  Additional imaging epochs will tell.

@@

\paragraph{Kepler-1643}
Kepler-1643~b (KOI-6186.01) was already validated as a transiting
planet by \citet{morton_false_2016}, who found a probability for any
of the aforementioned false positive scenarios of 9$\times$10$^{-6}$.
Repeating the calculation with our own stellar-variability correction
and the new NIRC2 imaging constraints, we find ${\rm FPP} =
6\times10^{-9}$, where the improvement is due to the new NIRC2
contrast curves.  Figure~\ref{fig:planets} shows the justification:
the transit is flat and has a high S/N ($\approx 47$), which is
difficult to reproduce with eclipsing binary models.

@@

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``candidate''
planet.  \citet{morton_false_2016} did not compute a false positive
probability for the system because their default trapezoidal fitting
routine failed, presumably due to the spot-induced variability.  Our
fitting approach rectifies this point, and our new NIRC2 images
revealed no new stellar companions.  Performing the validation
calculation, we find ${\rm FPP} \approx 4\times10^{-3}$.  Though not
as convincing as Kepler-1643, this formally clears the usual threshold
for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit is
$\approx$$32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve (see Figure~\ref{fig:planets}).
The positional probability score also meets the requirements for
transiting sources thought to share positions with their target stars
\citep{morton_false_2016,2017ksci.rept...16B}.
